---
title: "Calculate Percent Difference from LPS Dose (600, 200, or 70) vs LPS 0"
author: "EIF"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Libraries
```{r libraries}
library(rmarkdown)
library(openxlsx)
library(dplyr)
library(tidyverse)
library(psych)
library(ggplot2)
library(magrittr)
library(stats)
library(writexl)
library(ggpubr)
library(caret)
library(leaps)
library(MASS)
library(robustbase)
library(robustHD)
library(DescTools)

file_path = "/Users/flandree/Documents/02 UCSD Project/02. PercentDifferenceCytokine"
figure_path = "/Users/flandree/Documents/02 UCSD Project/02. PercentDifferenceCytokine"
```

#Import Data
```{r import data}
CytokineConcentration = read.xlsx(paste(file_path, "02 TransposeCytokineConcentrations.xlsx", sep = "/"), sheet = "TransposeImpute_LPSCyto")
```

#copy dataframe so i don't F up the original; only keep data columns
```{r Cyto Percent Change}
Cytokine_DF <- CytokineConcentration[,c(4:5,8,12:21)]
str(Cytokine_DF)
```

#Calculate Percent Change from cytokines
```{r Calculate Percent Change from cytokines}
PcntChange70_0 <- Cytokine_DF %>%
  group_by(Subject_ID, Visit_Number) %>%
  mutate(across(
    c(TNFalpha:IFNgamma),
    ~ ((. - .[LPS_DOSE == 0]) / .[LPS_DOSE == 0]) * 100,
    .names = "{.col}_PercentChange"
  )) %>%
  filter(LPS_DOSE == 70)

PcntChange200_0 <- Cytokine_DF %>%
  group_by(Subject_ID, Visit_Number) %>%
  mutate(across(
    c(TNFalpha:IFNgamma),
    ~ ((. - .[LPS_DOSE == 0]) / .[LPS_DOSE == 0]) * 100,
    .names = "{.col}_PercentChange"
  )) %>%
  filter(LPS_DOSE == 200)

PcntChange600_0 <- Cytokine_DF %>%
  group_by(Subject_ID, Visit_Number) %>%
  mutate(across(
    c(TNFalpha:IFNgamma),
    ~ ((. - .[LPS_DOSE == 0]) / .[LPS_DOSE == 0]) * 100,
    .names = "{.col}_PercentChange"
  )) %>%
  filter(LPS_DOSE == 600)
```

#bind the 3 percent change df together
#Cytokine_PcntChange2
```{r}
Cytokine_PcntChange <- rbind(PcntChange70_0, PcntChange200_0, PcntChange600_0)

Cytokine_PcntChange2 <- Cytokine_PcntChange[,c(1:3, 14:23)]
```


#Already Calculated percent change from baseline for each cytokine at each dose (70, 200, 600)
#add cytokine columns to instruction columns; 
#Write to file
#PcntChange_Labels
```{r Merge Cytokine and Info columns}
# Bind the percent change columns back to the original dataframe
PcntChange_Labels <- bind_cols(CytokineConcentration[CytokineConcentration$Sequence>230, c(1:10)], Cytokine_PcntChange[,c(14:23)])
str(PcntChange_Labels)

write_xlsx(PcntChange_Labels, "PcntChange_Labels.xlsx")
```

#scale the percent change data.  PcntChange_Zdf; write to file; plot histograms; NOTE, these data were not used in LMER calculations
```{r}
PcntChange_Z <- scale(PcntChange_Labels[,c(11:20)])

PcntChange_Zdf <- data.frame(PcntChange_Labels[,c(1:10)], PcntChange_Z)

str(PcntChange_Zdf)
write_xlsx(PcntChange_Zdf, "PcntChange_Zdf.xlsx")

#Value <- c("TNFalpha", "IL1beta", "IL2", "IL4", "IL6", "IL8", "IL10", "IL12p70", "IL13", "IFNgamma")
#TNFalpha_PercentChange, IL1beta_PercentChange, IL2_PercentChange, IL4_PercentChange,  IL6_PercentChange,IL8_PercentChange, IL10_PercentChange, #IL12p70_PercentChange, IL13_PercentChange, IFNgamma_PercentChange

data_columns <- c("TNFalpha_PercentChange", "IL1beta_PercentChange", "IL2_PercentChange",
                  "IL4_PercentChange", "IL6_PercentChange", "IL8_PercentChange",
                  "IL10_PercentChange", "IL12p70_PercentChange", "IL13_PercentChange",
                  "IFNgamma_PercentChange")

# Reshape data from wide to long format
df_long <- tidyr::pivot_longer(PcntChange_Zdf, cols = all_of(data_columns), 
                              names_to = "Cytokine", values_to = "Value")

# Create faceted histograms colored by LPS_DOSE
hist_plot <- ggplot(df_long, aes(x = Value, fill = factor(LPS_DOSE))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 75) +
  facet_wrap(~ Cytokine, scales = "free") +
  scale_fill_manual(values = c("blue", "red", "green")) +
  scale_color_manual(values = c("blue", "red", "green"))
  labs(fill = "LPS Dose") +
  theme_bw()

ggsave("cytokine_histograms2.pdf", plot = hist_plot, 
       width = 16, height = 12, units = "in", dpi = 300)

# Save as PNG (raster format)
ggsave("cytokine_histograms.png", plot = hist_plot,
       width = 16, height = 12, units = "in", dpi = 600)

hist_plot

# Create faceted histograms colored by LPS_DOSE
hist_plot <- ggplot(df_long, aes(x = Value, fill = factor(LPS_DOSE))) +
  geom_histogram(position = "dodge", alpha = 0.8, bins = 30) +
  facet_wrap(~ Cytokine, scales = "free") +
  scale_fill_manual(values = c("blue", "red", "green")) +
  scale_color_manual(values = c("darkblue", "darkred", "darkgreen", linewidth = 1)) 
  labs(fill = "LPS Dose") +
  theme_bw()

ggsave("cytokine_histograms4.pdf", plot = hist_plot, 
       width = 16, height = 12, units = "in", dpi = 300)

hist_plot
```


#IMPORT DATA
#cytokine concentration data -->  percent change from LPS0 NOTE: THESE DATA ARE NOT SCALED
```{r import data}
PcntChangeCytokines = read.xlsx(paste(file_path, "02 TransposePcntChange.xlsx", sep = "/"), sheet = "PcntChangeImputeCyto")

str(PcntChangeCytokines)
```

#modify structure
#PcntChangeCytokines (df)
```{r}
df <- PcntChangeCytokines[,c(1:21)]

df[,c(4:11)] <- lapply(PcntChangeCytokines[,c(4:11)], as.factor)
str(df)

```

#Histograms of pcnt difference cytokines
#df2
```{r}
df2 <- df

TNFalpha <- ggplot(data=df2) +
  geom_histogram(aes(x=TNFalpha, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL1beta <- ggplot(data=df2) +
  geom_histogram(aes(x=IL1beta, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL6 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL6, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL8 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL8, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL10 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL10, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL12p70 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL12p70, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL13 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL13, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IFNgamma <- ggplot(data=df2) +
  geom_histogram(aes(x=IFNgamma, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL2 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL2, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
IL4 <- ggplot(data=df2) +
  geom_histogram(aes(x=IL4, fill=Pcntvs0))+
  facet_wrap(~Visit_Number)
```

#Subset df to include only cytokines; 
```{r}
Cytokines <-subset(df[,c(12:21)])
```

#scale cytokines and plot; Z Score didn't do much to normalize the data.
#VERIFY THAT Z SCORE DOESN"T NORMALIZE DATA MUCH
```{r}
# Zdf2 <- scale(Cytokines)
# 
# zTNFalpha <- ggplot(data=Zdf2) +
#    geom_histogram(aes(x=TNFalpha, fill=Pcntvs0))+
#    facet_wrap(~Visit_Number)
#  
# zIL1beta <- ggplot(data=Zdf2) +
#    geom_histogram(aes(x=IL1beta, fill=Pcntvs0))+
#    facet_wrap(~Visit_Number)
#  
# zIL6 <- ggplot(data=Zdf2) +
#    geom_histogram(aes(x=IL6, fill=Pcntvs0))+
#    facet_wrap(~Visit_Number)
# 
# zIL8 <- ggplot(data=Zdf2) +
#    geom_histogram(aes(x=IL8, fill=Pcntvs0))+
#    facet_wrap(~Visit_Number)
```

#Winsorize
```{r}
Cytokines_Wins <-winsorize(Cytokines, thresh=c(0.01, 0.99),na.rm=FALSE)
head(Cytokines_Wins)
```


#Add winsorized percent change cytokine data to experimental column info
```{r}
Cytokines_Wins <- data.frame(Cytokines_Wins)
PcntDiff_Wins <- cbind(df2[,c(1:11)], Cytokines_Wins)
```

#load covariate data; PcntDiffWins_CoVars #write to file
```{r}
CoVars = read.xlsx(paste(file_path, "02 CoVars for TransposePcntChange.xlsx", sep = "/"), sheet = "CoVars")
str(CoVars)

PcntDiffWins_CoVars <- merge(PcntDiff_Wins, CoVars, by = "Sequence")
str(PcntDiffWins_CoVars)
```
#load dataframe #PcntDiffWins_CoVars #df
```{r }
df <- read.xlsx("PcntDiffWins_CoVars.xlsx", colNames = TRUE)
#str(df)
```

#Update variable structure; PcntDiffWins_CoVars #df; df2
```{r update relevant variables to factors}
#copy dataframes so I don't mess them up

df <- PcntDiffWins_CoVars
df2 <- df

df2[,c(6:11,28, 30:47)] <- lapply(df2[,c(6:11,28, 30:47)], as.factor)
df2$Pcntvs0 <- relevel(df2$Pcntvs0, ref = "70")
str(df2)
```


```{r Generate Tables of DemographicData}
table(df2$Pcntvs0)


visit_counts <- df2 %>%
  group_by(Visit_Number, Age_Cat) %>%
  summarise(n_subjects = n_distinct(Subject_ID), .groups = "drop")

visit_counts
```

#write to file
```{r}
PcntDiffWins_CoVars <- df2
write.xlsx(PcntDiffWins_CoVars, "PcntDiffWins_CoVars.xlsx", colNames = TRUE)
```


