---
title: "4.30.25"
author: "EIF"
date: "`r Sys.Date()`"
output: html_document
---
#Cytokine pcnt difference 600-0 with all mood factors, Anxiety seems to play a role; Individual mood factors, GI may be important.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Libraries
```{r libraries}
library(rmarkdown)
library(openxlsx)
library(dplyr)
library(tidyverse)
library(psych)
library(ggplot2)
library(magrittr)
library(stats)
library(writexl)
library(ggpubr)
library(caret)
library(leaps)
library(MASS)
library(robustbase)
library(robustHD)
library(DescTools)
library(lme4)
library(lmerTest)
library(nlme)
library(interactions)
library(ds4psy)
library(sjPlot)
library(ggeffects)
library(emmeans)
library(effects)

file_path = "/Users/flandree/Documents/02 UCSD Project/2026 Reanalysis"
figure_path = "/Users/flandree/Documents/02 UCSD Project/2026 Reanalysis"
```

#load dataframe and update structure
```{r }
df <- read.xlsx("PcntDiffWins_CoVars.xlsx", colNames = TRUE)

df <- df %>%
  mutate(across(where(is.character), as.factor))
df$Pcntvs0 <- relevel(df$Pcntvs0, ref = "70")

str(df)
```

#Create tables of demographic info
```{r Tables}
table(df$Pcntvs0)


visit_counts <- df %>%
  group_by(Visit_Number, Age_Cat) %>%
  summarize(n_subjects = n_distinct(Subject_ID), .groups = "drop")

visit_counts
```


#use the dataframe PcntDiffWins_CoVars
#separate by doses, visit, age, and gender for graphing
```{r subset by LPS dose vs. 0}
df2 <- df

PcntChange70 <- subset(df2, Pcntvs0 == 70)
PcntChange200 <- subset(df2, Pcntvs0 == 200)
PcntChange600 <- subset(df2, Pcntvs0 == 600)

PcntChangeVisit1 <- subset(df2, Visit_Number == 1)
PcntChangeVisit2 <- subset(df2, Visit_Number == 2)
PcntChangeVisit3 <- subset(df2, Visit_Number == 3)

AgeCat1 <- subset(df2, Age_Cat == 1)
AgeCat2 <- subset(df2, Age_Cat == 2)
AgeCat3 <- subset(df2, Age_Cat == 3)
AgeCat4 <- subset(df2, Age_Cat == 4)

PcntChange_Male <- subset(df2, Gender == 1)
PcntChange_Female <- subset(df2, Gender == 2)

table(df2$Gender)
table(PcntChange_Male$Gender)
table(AgeCat1$Gender)

```

#Notes: (1|Subject_ID:Pcntvs0) models a random intercept for each unique combination of Subject_ID and Pcntvs0. This leads to a finer grouping factor with many levels (number of subjects × number of Pcntvs0 levels), which can be less conservative as it pools less information across subjects and conditions. It can also be more complex and harder to interpret because the variance is attributed to these interaction-level units.
#(1|Subject_ID) + (1|Pcntvs0) models two independent random intercepts: one for subjects and one for the factor Pcntvs0. This partitions the variance into between-subject variability and between-level (of Pcntvs0) variability separately. This is more straightforward in interpretation since it treats the effects as additive random intercepts, each with their own variance component. It is also usually more conservative because it shrinks estimates more strongly toward overall means before estimating interaction variability.
#(1|Subject_ID) + (1|Subject_ID:Visit_Number) + (1|Pcntvs0) #IFNgamma & IL10
#===================================================================================================#
#Experimental variables for all cytokines
#===================================================================================================#
```{r experimental variables}
#Identify which experimental variables significantly influence individual cytokines; any that are significant need to be considered in future models.

IL1betaA <- lmer(IL1beta ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge + Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL1betaA) # batch, silanized LPS
#LPS_Batch2     -1178.203    286.770   306.540  -4.109 5.12e-05 ***
#silanized_LPS1   894.222    300.456   407.654   2.976  0.00309 ** 
#silanized_LPS2  1570.705    316.714   409.648   4.959 1.04e-06 ***
#===================================================================================================#
IL2a <- lmer(IL2 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge + Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL2a) #batch, plate, project
   
# LPS_Batch3       73.1396    30.9482  318.4849   2.363 0.018714 *  
# LPS_Batch5      113.2290    35.3588  201.3548   3.202 0.001585 ** 
# Project15      -111.1063    23.9316   49.4563  -4.643 2.56e-05 ***
# Project9       -102.9786    42.9860   62.5324  -2.396 0.019598 *  
# Plate6          -81.0168    45.9355   47.3471  -1.764 0.084233 .  
# Plate8         -109.0525    49.3585   45.3018  -2.209 0.032244 * 
#===================================================================================================#
IL4a <- lmer(IL4 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge + Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL4a) #batch, project, silanized, visit

# LPS_Batch3      295.0803    71.4254  354.1639   4.131 4.51e-05 ***
# LPS_Batch4      172.0930    56.8854  149.6008   3.025  0.00293 ** 
# LPS_Batch5      215.8807    84.5093  241.5937   2.555  0.01125 *  
# Project15      -167.8890    65.6827   49.6483  -2.556  0.01369 *  
# silanized_LPS2  184.4391    46.3562  404.8108   3.979 8.21e-05 ***
# Visit_Number2   -69.3392    23.0277  425.8301  -3.011  0.00276 ** 
#===================================================================================================#
IL6a <- lmer(IL6 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge + Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL6a) #batch, silanized

# LPS_Batch2     -4096.24    1557.66   302.85  -2.630  0.00898 ** 
# LPS_Batch3      8172.05    2597.65   347.61   3.146  0.00180 ** 
# LPS_Batch4      8132.05    2055.46   140.25   3.956  0.00012 ***
# silanized_LPS2  5557.80    1694.18   404.65   3.281  0.00113 ** 
#===================================================================================================#
IL8a <- lmer(IL8 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge + Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL8a) #visit, plate, batch
# LPS_Batch2     -251.811     86.706  289.447  -2.904  0.00397 ** 
# LPS_Batch3      259.922    145.526  334.132   1.786  0.07499 .  
# LPS_Batch4      312.194    110.759  125.523   2.819  0.00560 ** 
# Plate7          535.961    247.746   45.742   2.163  0.03578 *  
# silanized_LPS2  244.334     97.634  411.098   2.503  0.01272 *  
# Visit_Number2   106.987     48.121  426.082   2.223  0.02672 *  
# Visit_Number3   199.781     65.296  420.604   3.060  0.00236 ** 

#===================================================================================================#
IL10a <- lmer(IL10 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge +Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL10a) #batch, silanized, project
#  
# LPS_Batch3      189.9755    55.0243  329.1854   3.453 0.000628 ***
# LPS_Batch4       89.4707    41.6136  120.1671   2.150 0.033556 *  
# Project15      -129.7371    44.9124   49.2281  -2.889 0.005736 ** 
# Plate8         -165.8526    92.9336   45.4713  -1.785 0.080993 .  
# silanized_LPS2  126.1644    37.0816  411.4266   3.402 0.000734 ***

#===================================================================================================#
IL12p70a <- lmer(IL12p70 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge +Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL12p70a) #batch, project
# LPS_Batch2      -82.393     35.315  331.150  -2.333   0.0202 *  
# Project15      -261.571     56.849   53.707  -4.601 2.60e-05 ***
# Project9       -172.004     99.270   62.202  -1.733   0.0881 . 
#===================================================================================================#
IL13a <- lmer(IL13 ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge + Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IL13a) #visit, plate, project, batch
# LPS_Batch3       68.2351    25.2220  335.7354   2.705  0.00717 ** 
# LPS_Batch4       45.4224    19.0663  128.0363   2.382  0.01867 *  
# Project15      -123.5735    20.5675   53.3590  -6.008 1.72e-07 ***
# Project9        -82.3603    36.6493   65.6517  -2.247  0.02799 *  
# Plate8         -107.7207    42.5563   49.3215  -2.531  0.01460 *  
# Visit_Number2    18.2185     8.3721  426.1418   2.176  0.03010 *  
# Visit_Number3    25.2700    11.3473  420.5844   2.227  0.02648 * 
#===================================================================================================#
TNFalphaA <- lmer(TNFalpha ~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge +Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(TNFalphaA) # batch, silanized
# LPS_Batch2     -2454.83     701.51   286.70  -3.499 0.000541 ***
# LPS_Batch4      3012.96     902.25   123.23   3.339 0.001111 ** 
# silanized_LPS2  2924.64     784.35   408.95   3.729 0.000220 ***
# Visit_Number2    677.75     387.06   426.00   1.751 0.080665 .  
#===================================================================================================#
IFNgammaA <- lmer(IFNgamma~ LPS_Batch + Project + Plate + silanized_LPS + Visit_Number + Gender + ApproxAge +Pcntvs0 +
                     (1|Subject_ID), data = df2)
summary(IFNgammaA) #silanized, batch
# LPS_Batch4      34.8194    17.0049 120.1695   2.048 0.042778 *  
# silanized_LPS1  43.2390    14.4320 409.8003   2.996 0.002901 ** 
# silanized_LPS2  54.0518    15.2071 411.8323   3.554 0.000423 ***
#===================================================================================================#
```

#===================================================================================================
#box plots for experimental variables
```{r}
boxplot(IL1beta ~ LPS_Batch, data = df2)
boxplot(IL1beta ~ silanized_LPS, data = df2)

boxplot(IL2 ~ LPS_Batch, data = df2)
boxplot(IL2 ~ Project, data = df2)

boxplot(IL4 ~ LPS_Batch, data = df2)
boxplot(IL4 ~ silanized_LPS, data = df2)
boxplot(IL4 ~ Visit_Number, data = df2)

boxplot(IL6 ~ LPS_Batch, data = df2)
boxplot(IL6 ~ silanized_LPS, data = df2)

boxplot(IL8 ~ LPS_Batch, data = df2)
boxplot(IL8 ~ silanized_LPS, data = df2)
boxplot(IL8 ~ Visit_Number, data = df2)

boxplot(IL10 ~ LPS_Batch, data = df2)
boxplot(IL10 ~ silanized_LPS, data = df2)
boxplot(IL10 ~ Project, data = df2)

boxplot(IL12p70 ~ LPS_Batch, data = df2)
boxplot(IL12p70 ~ Project, data = df2)

boxplot(IL13 ~ LPS_Batch, data = df2)
boxplot(IL13 ~ Project, data = df2)
boxplot(IL13 ~ Visit_Number, data = df2)

boxplot(TNFalpha ~ LPS_Batch, data = df2)
boxplot(TNFalpha ~ silanized_LPS, data = df2)

```
#===================================================================================================#


#anhedonia not significant IL2, IL4, Il10, 12, 13, TNFalpha
```{r}
#=============================================================================================
#IL2 anhedonia
m1 <- lmer(IL2 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1 | Subject_ID:LPS_Batch),
           data = df2, REML = FALSE)

m2 <- lmer(IL2 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1 | Subject_ID) + (1 | LPS_Batch),
           data = df2, REML = FALSE)

anova(m1, m2)
#m1    8 5472.8 5505.7 -2728.4    5456.8                     
#m2    9 5473.4 5510.4 -2727.7    5455.4 1.4296  1     0.2318 #format of random factors doesn't matter

summary(m1)
summary(m2)
#
```

#IL4 Anhedonia
```{r}
#=============================================================================================
IL4 <- lmer(IL4 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID) + (1|LPS_Batch) + (1|silanized_LPS), data = df2)
summary(IL4) #anhedonia ns; visit 2 sig
#
m1 <- lmer(IL4 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID) + (1|LPS_Batch) + (1|silanized_LPS), data = df2, REML = FALSE)

m2 <- lmer(IL4 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2, REML = FALSE)
anova(m1, m2)
#=============================================================================================
#m2   12 6224.1 6273.5 -3100.1    6200.1                         
#m1   14 6180.3 6237.9 -3076.2    6152.3 47.796  2   4.18e-11 *** <- m1 is the better model

summary(m1)
#Anhedonia            -182.669    102.031  284.172  -1.790   0.0745 .  
# Pcntvs0200            130.727     22.860  339.658   5.719 2.35e-08 ***
# Pcntvs0600            280.790     22.423  368.616  12.523  < 2e-16 ***
# ApproxAge               2.455      1.829   65.562   1.343   0.1840    
# Anhedonia:Pcntvs0200   14.554     29.075  370.776   0.501   0.6170    
# Anhedonia:Pcntvs0600   20.098     29.053  370.549   0.692   0.4895    
# Anhedonia:ApproxAge     3.581      2.143  332.426   1.671   0.0956 . 

summary(m2)
# Anhedonia            -184.387    103.453  310.209  -1.782   0.0757 .  
# Pcntvs0200            123.558     21.947  345.181   5.630 3.74e-08 ***
# Pcntvs0600            269.310     21.787  337.466  12.361  < 2e-16 ***
# ApproxAge               1.627      1.592  142.040   1.023   0.3082    
# Anhedonia:Pcntvs0200    6.685     30.284  349.414   0.221   0.8254    
# Anhedonia:Pcntvs0600   14.112     30.109  343.503   0.469   0.6396    
# Anhedonia:ApproxAge     4.209      2.241  339.956   1.878   0.0612 . 
```

#IL10 and anhedonia
```{r IL10}
m1 <- lmer(IL10 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + 
             (1 | Subject_ID:LPS_Batch:silanized_LPS),
           data = df2, REML = FALSE)

m2 <- lmer(IL10 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge +
             (1 | Subject_ID) + (1 | LPS_Batch) + (1 | silanized_LPS),
           data = df2, REML = FALSE)

anova(m1, m2)

#    npar    AIC    BIC  logLik -2*log(L)  Chisq Df Pr(>Chisq)    
# m1   12 6017.4 6066.8 -2996.7    5993.4                         
# m2   14 5971.3 6029.0 -2971.7    5943.3 50.085  2  1.331e-11 *** <- model 2 is better

summary(m1)
# Anhedonia                  7.574     26.647 403.014   0.284   0.7764    
# Pcntvs0200               113.053     17.966 345.511   6.292 9.46e-10 ***
# Pcntvs0600               168.925     17.870 337.659   9.453  < 2e-16 ***
# Visit_Number2             42.871     19.762 445.935   2.169   0.0306 *  
# Visit_Number3              7.018     26.962 436.721   0.260   0.7948    
# Anhedonia:Pcntvs0200       8.837     24.768 351.649   0.357   0.7215    
# Anhedonia:Pcntvs0600      11.675     24.658 345.590   0.473   0.6362    
# Anhedonia:Visit_Number2    1.586     26.966 445.949   0.059   0.9531    
# Anhedonia:Visit_Number3    9.051     38.181 436.468   0.237   0.8127    

summary(m2)
# Anhedonia                 -5.783     24.866 403.391  -0.233  0.81623    
# Pcntvs0200               120.312     18.195 329.995   6.612 1.52e-10 ***
# Pcntvs0600               176.910     17.860 366.003   9.905  < 2e-16 ***
# Visit_Number2             26.404     17.589 413.579   1.501  0.13409    
# Visit_Number3             12.948     24.184 365.610   0.535  0.59271    
# Anhedonia:Pcntvs0200      13.708     23.178 370.222   0.591  0.55459    
# Anhedonia:Pcntvs0600      12.415     23.161 369.959   0.536  0.59227    
# Anhedonia:Visit_Number2   -5.226     23.666 423.168  -0.221  0.82535    
# Anhedonia:Visit_Number3   25.997     33.041 446.605   0.787  0.43180

# Anhedonia             -60.047     78.342 255.577  -0.766   0.4441    
# Pcntvs0200            120.132     18.304 332.681   6.563 2.02e-10 ***
# Pcntvs0600            177.957     17.955 366.269   9.912  < 2e-16 ***
# ApproxAge               2.400      1.330  64.698   1.805   0.0758 .  
# Anhedonia:Pcntvs0200   13.662     23.307 369.197   0.586   0.5581    
# Anhedonia:Pcntvs0600   12.686     23.288 368.938   0.545   0.5863    
# Anhedonia:ApproxAge     1.265      1.654 301.006   0.765   0.4450 

```

#IL12p70 anhedonia
```{r}
#=============================================================================================
IL12p70 <- lmer(IL12p70 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL12p70) #ns
# 

Anhedonia_IL12p70 <- lmer(IL12p70 ~ Anhedonia*Pcntvs0 + (1|Subject_ID:LPS_Batch:silanized_LPS), 
            data = df2)
summary(Anhedonia_IL12p70)

m1 <- lmer(IL12p70 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2, REML = FALSE)

m2 <- lmer(IL12p70 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1 | Subject_ID) + (1 | LPS_Batch) + (1 | silanized_LPS), data = df2, REML = FALSE)

anova(m1, m2)
#m2   12 5987.1 6036.5 -2981.5    5963.1 34.268  2  3.621e-08 *** model failed to converge

summary(m2) #ns

# Pcntvs0200            112.966     16.695  362.045   6.767 5.32e-11 ***
# Pcntvs0600            176.480     16.695  362.048  10.571  < 2e-16 ***
# ApproxAge               4.339      1.798   70.304   2.413   0.0184 *  
# Anhedonia:Pcntvs0200   13.730     22.758  376.609   0.603   0.5467    
# Anhedonia:Pcntvs0600   39.438     22.758  376.609   1.733   0.0839 .  
# Anhedonia:ApproxAge     3.507      1.797  404.265   1.952   0.0517 .  

summary(m1)
# Anhedonia            -110.468     87.525  363.607  -1.262   0.2077    
# Pcntvs0200            116.752     16.484  333.093   7.083 8.45e-12 ***
# Pcntvs0600            179.381     16.324  326.672  10.989  < 2e-16 ***
# ApproxAge               3.614      1.473  144.788   2.453   0.0153 *  
# Anhedonia:Pcntvs0200   16.885     22.771  335.245   0.742   0.4589    
# Anhedonia:Pcntvs0600   42.998     22.596  330.389   1.903   0.0579 .  
# Anhedonia:ApproxAge     2.875      1.872  402.572   1.536   0.1254
```

#IL13, anhedonia
```{r}
#=============================================================================================
IL13 <- lmer(IL13 ~ Anhedonia*Pcntvs0 + 
               (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL13) #ns visit, age, or anhedonia
#
```


```{r}
#=============================================================================================
TNFalpha <- lmer(TNFalpha ~ Anhedonia*Pcntvs0 + 
                   (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(TNFalpha) 
# 
```

#Anhedonia& IL1beta
```{r}
#=============================================================================================
IL1beta <- lmer(IL1beta ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL1beta) 
# Anhedonia            -2306.6262   719.9773   308.9070  -3.204  0.00150 ** 
# Pcntvs0200            1016.9915   146.9513   326.8586   6.921 2.38e-11 ***
# Pcntvs0600            1693.6950   145.7626   319.1881  11.620  < 2e-16 ***
# ApproxAge                8.8602    11.3703   129.1444   0.779  0.43726    
# Anhedonia:Pcntvs0200    38.3350   202.8636   330.4684   0.189  0.85023    
# Anhedonia:Pcntvs0600     0.5907   201.5608   324.6034   0.003  0.99766    
# Anhedonia:ApproxAge     51.0930    15.5392   344.3259   3.288  0.00111 ** 

Anhedonia_IL1beta <- lmer(IL1beta ~ Anhedonia*Pcntvs0 + Anhedonia*Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(Anhedonia_IL1beta) 
# Anhedonia            -691.780    321.727  277.132  -2.150 0.032404 *  
# Pcntvs0200           1016.996    146.560  326.714   6.939 2.13e-11 ***
# Pcntvs0600           1690.276    145.409  319.445  11.624  < 2e-16 ***
# Anhedonia:Age_Cat3    985.654    413.528  287.049   2.384 0.017798 *  
# Anhedonia:Age_Cat4   2091.412    555.151  347.881   3.767 0.000194 ***

slopes <- emtrends(Anhedonia_IL1beta, ~ Age_Cat, var = "Anhedonia", cov.red = FALSE)
test(slopes)
 # Age_Cat Anhedonia.trend  SE  df t.ratio p.value
 # 1                  -680 302 243  -2.255  0.0250 *
 # 2                  -181 298 328  -0.608  0.5435
 # 3                   305 289 352   1.058  0.2906
 # 4                  1411 470 401   3.006  0.0028 **

eff <- ggeffect(Anhedonia_IL1beta, terms = c("Anhedonia", "Age_Cat"))
plot(eff)+ labs(x = "PTSD", y = "TNFalpha", title = "TNFalpha by PTSD across Age_Cat")+ theme_minimal()
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Anhedonia",
       y = "Predicted IL1beta",
       title = "IL1beta vs Anhedonia by Age Category") +
  theme_minimal()

```

#Anhedonia, IL6
```{r}
#=============================================================================================
IL6 <- lmer(IL6 ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL6) 
# #Anhedonia            -9385.02    3783.94   321.88  -2.480  0.01364 *  
# Pcntvs0200            6420.40     766.61   334.97   8.375 1.53e-15 ***
# Pcntvs0600           12925.75     760.29   327.75  17.001  < 2e-16 ***
# ApproxAge              -17.09      60.08   139.18  -0.284  0.77647    
# Anhedonia:Pcntvs0200  -782.84    1058.36   338.27  -0.740  0.46001    
# Anhedonia:Pcntvs0600 -1183.70    1051.44   332.76  -1.126  0.26107    
# Anhedonia:ApproxAge    211.80      81.61   356.26   2.595  0.00984 ** 

Anhedonia_IL6 <- lmer(IL6 ~ Anhedonia*Pcntvs0 + Anhedonia * Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(Anhedonia_IL6)
# #Anhedonia             -4016.5     1693.1   289.0  -2.372  0.01833 *  
# Pcntvs0200             6422.8      763.3   332.8   8.415 1.18e-15 ***
# Pcntvs0600            12937.6      757.1   326.0  17.088  < 2e-16 ***
# Age_Cat2                305.0     1809.9   280.4   0.169  0.86628    
# Age_Cat3               1076.3     1939.9   179.2   0.555  0.57971    
# Age_Cat4              -1904.9     2165.5   157.3  -0.880  0.38040    
# Anhedonia:Pcntvs0200   -783.7     1053.8   336.1  -0.744  0.45759    
# Anhedonia:Pcntvs0600  -1187.3     1046.9   330.7  -1.134  0.25756    
# Anhedonia:Age_Cat2     3482.6     2108.2   339.1   1.652  0.09947 .  
# Anhedonia:Age_Cat3     6746.6     2175.5   300.8   3.101  0.00211 ** 
# Anhedonia:Age_Cat4     6499.3     2915.7   359.3   2.229  0.02643 * 

#test slopes for Anhedonia*Age Relationship
slopes <- emtrends(Anhedonia_IL6, ~ Age_Cat, var = "Anhedonia", cov.red = FALSE)
test(slopes)
# Age_Cat Anhedonia.trend   SE  df t.ratio p.value
#  1                 -4674 1590 248  -2.940  0.0036 **
#  2                 -1191 1570 331  -0.761  0.4474
#  3                  2073 1520 358   1.368  0.1723
#  4                  1826 2460 406   0.741  0.4588

eff <- ggeffect(Anhedonia_IL6, terms = c("Anhedonia", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Anhedonia",
       y = "Predicted IL6",
       title = "IL6 vs Anhedonia by Age Category") +
  theme_minimal()
```

#IL8 Anhedonia
```{r}
#=============================================================================================
IL8 <- lmer(IL8 ~ Anhedonia*Pcntvs0 + Anhedonia*Visit_Number + Anhedonia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS),
            data = df2)
summary(IL8)
# Anhedonia               -483.278    207.284  338.450  -2.331  0.02031 *  
# Pcntvs0200               297.493     40.357  326.870   7.372 1.39e-12 ***
# Pcntvs0600               584.885     40.026  320.496  14.612  < 2e-16 ***
# Visit_Number2            102.081     46.367  403.146   2.202  0.02826 *  
# Visit_Number3            146.657     65.931  440.966   2.224  0.02663 *  
# ApproxAge                  6.049      3.356  137.774   1.803  0.07365 .  
# Anhedonia:Pcntvs0200     -19.930     55.732  329.594  -0.358  0.72087    
# Anhedonia:Pcntvs0600      -2.782     55.362  324.760  -0.050  0.95995    
# Anhedonia:Visit_Number2 -108.096     63.397  401.941  -1.705  0.08895 .  
# Anhedonia:Visit_Number3 -280.911     92.960  440.995  -3.022  0.00266 ** 
# Anhedonia:ApproxAge       12.196      4.459  366.812   2.735  0.00654 ** 

IL8 <- lmer(IL8 ~ Anhedonia*Pcntvs0 + Anhedonia* ApproxAge + (1|Subject_ID/Visit_Number:LPS_Batch:silanized_LPS), 
            data = df2)
summary(IL8)
# Anhedonia            -653.046    265.231  137.589  -2.462    0.015 *  
# Pcntvs0200            293.730     36.230  285.698   8.107 1.53e-14 ***
# Pcntvs0600            576.767     36.230  285.698  15.919  < 2e-16 ***
# ApproxAge               8.067      3.729   69.218   2.163    0.034 *  
# Anhedonia:Pcntvs0200  -19.086     49.880  291.355  -0.383    0.702    
# Anhedonia:Pcntvs0600   -8.115     49.880  291.355  -0.163    0.871    
# Anhedonia:ApproxAge    14.123      5.851  153.271   2.414    0.017 * 


Anhedonia_IL8 <- lmer(IL8 ~ Anhedonia*Pcntvs0 + Anhedonia*Age_Cat + (1|Subject_ID/Visit_Number:LPS_Batch:silanized_LPS), 
            data = df2)
summary(Anhedonia_IL8)
# Anhedonia            -238.794    110.532  118.676  -2.160   0.0328 *  
# Anhedonia:Age_Cat3    323.158    149.404  135.310   2.163   0.0323 *  
# Anhedonia:Age_Cat4    523.075    209.219  168.248   2.500   0.0134 * 

#If you have a mixed model (e.g., lmer), use the same approach on the fitted model object:

#Evaluate slopes 
slopes <- emtrends(Anhedonia_IL8, ~ Age_Cat, var = "Anhedonia", cov.red = FALSE)
test(slopes)
#Age_Cat Anhedonia.trend  SE  df t.ratio p.value
 # 1                -247.9 108 102  -2.298  0.0236 *
 # 2                -116.8 114 145  -1.025  0.3070
 # 3                  75.3 106 163   0.711  0.4782
 # 4                 275.2 182 177   1.511  0.1325
 
#Plot the Interaction
eff <- ggeffect(Anhedonia_IL8, terms = c("Anhedonia", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Anhedonia",
       y = "Predicted IL8",
       title = "IL8 vs Anhedonia by Age Category") +
  theme_minimal()
```


#anhedonia IFNgamma, age
```{r}
#=============================================================================================
IFNgamma <- lmer(IFNgamma ~ Anhedonia*Pcntvs0 + Anhedonia*ApproxAge + 
                   (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IFNgamma)
#Anhedonia            -97.2570    32.1666 289.0997  -3.024 0.002722 ** 
# Pcntvs0200            26.3452     6.6960 319.3033   3.934 0.000102 ***
# Pcntvs0600            32.4983     6.6446 311.0503   4.891 1.61e-06 ***
# ApproxAge              1.6163     0.5011 118.7735   3.226 0.001624 ** 
# Anhedonia:Pcntvs0200   1.2236     9.2418 323.5235   0.132 0.894748    
# Anhedonia:Pcntvs0600   3.8806     9.1854 317.1834   0.422 0.672961    
# Anhedonia:ApproxAge    2.2983     0.6955 323.6331   3.304 0.001058 ** 

IFNgamma <- lmer(IFNgamma ~ Anhedonia*Pcntvs0 +  
                   (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IFNgamma) #ns without age in model

Anhedonia_IFNgamma  <- lmer(IFNgamma  ~ Anhedonia * Age_Cat + (1|Subject_ID), data = df2)
summary(Anhedonia_IFNgamma)
# Anhedonia            -14.95      13.09 141.70  -1.142 0.255395    
# Age_Cat2              14.62      16.02 124.27   0.912 0.363435    
# Age_Cat3              26.99      17.18  77.85   1.571 0.120207    
# Age_Cat4              37.41      18.30  82.62   2.044 0.044111 *  
# Anhedonia:Age_Cat2    12.77      17.81 228.28   0.717 0.474044    
# Anhedonia:Age_Cat3    14.34      17.50 205.65   0.820 0.413373    
# Anhedonia:Age_Cat4    84.45      23.71 301.13   3.561 0.000429 ***

eff <- ggeffect(Anhedonia_IFNgamma , terms = c("Anhedonia", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Anhedonia",
       y = "Predicted IFNgamma ",
       title = "IFNgamma  vs Anhedonia by Age Category") +
  theme_minimal()

slopes <- emtrends(Anhedonia_IFNgamma, ~ Age_Cat, var = "Anhedonia", cov.red = FALSE)
test(slopes)
 # Age_Cat Anhedonia.trend   SE  df t.ratio p.value
 # 1               -14.952 13.2 147  -1.133  0.2591
 # 2                -2.183 13.4 233  -0.162  0.8711
 # 3                -0.612 11.8 318  -0.052  0.9586
 # 4                69.500 19.9 398   3.491  0.0005

```
#===================================================================================================#
#===================================================================================================#
#PTSD IL1beta
```{r}
IL1beta <- lmer(IL1beta ~ PTSD*Pcntvs0 + PTSD*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL1beta) #
# #PTSD            -1596.403    658.800   382.602  -2.423   0.0158 *  
# Pcntvs0200       1021.176    147.490   326.944   6.924 2.34e-11 ***
# Pcntvs0600       1713.330    146.093   318.598  11.728  < 2e-16 ***
# ApproxAge           5.120     11.543   129.812   0.444   0.6581    
# PTSD:Pcntvs0200    39.179    210.408   328.500   0.186   0.8524    
# PTSD:Pcntvs0600     4.229    208.925   322.161   0.020   0.9839    
# PTSD:ApproxAge     36.355     14.790   353.458   2.458   0.0144 *  

PTSD_IL1beta  <- lmer(IL1beta  ~ PTSD*Pcntvs0 + PTSD*Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(PTSD_IL1beta)
# PTSD            -617.384    300.376  401.909  -2.055 0.040489 *  
# PTSD:Age_Cat3    742.437    433.869  302.588   1.711 0.088068 .  
# PTSD:Age_Cat4   1988.848    559.695  289.315   3.553 0.000444 ***

slopes <- emtrends(PTSD_IL1beta, ~ Age_Cat, var = "PTSD", cov.red = FALSE)
test(slopes)
 # Age_Cat PTSD.trend  SE  df t.ratio p.value
 # 1           -604.0 277 369  -2.184  0.0296 *
 # 2             12.7 307 330   0.041  0.9671
 # 3            138.5 338 275   0.409  0.6826
 # 4           1384.9 490 281   2.826  0.0050 **

eff <- ggeffect(PTSD_IL1beta , terms = c("PTSD", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL1beta ",
       title = "IL1beta  vs PTSD by Age Category") +
  theme_minimal()
```

#PTSD_IL4
```{r}
PTSD_IL4 <- lmer(IL4 ~ PTSD*Pcntvs0 + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(PTSD_IL4) 
# PTSD             78.5650    29.6604 405.1517   2.649  0.00839 ** 
# Pcntvs0200      122.8516    22.0628 346.7427   5.568 5.16e-08 ***
# Pcntvs0600      269.7965    21.8826 338.2670  12.329  < 2e-16 ***
# PTSD:Pcntvs0200  -0.5007    31.4650 348.7085  -0.016  0.98731    
# PTSD:Pcntvs0600  22.1187    31.2778 342.3750   0.707  0.47994  

eff <- ggeffect(PTSD_IL4 , terms = "PTSD")
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL4",
       title = "IL4  vs PTSD") +
  theme_minimal()
```

#PTSD IL6
```{r}
#=============================================================================================
IL6 <- lmer(IL6 ~ PTSD*Pcntvs0 + PTSD*ApproxAge + 
              (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL6)  # no effect of visit #
# #PTSD            -9284.05    3434.72   389.28  -2.703  0.00717 ** 
# Pcntvs0200       6458.55     766.72   334.43   8.424 1.09e-15 ***
# Pcntvs0600      13061.99     759.40   326.48  17.200  < 2e-16 ***
# ApproxAge         -20.04      60.39   138.57  -0.332  0.74043    
# PTSD:Pcntvs0200  -345.71    1093.82   335.89  -0.316  0.75215    
# PTSD:Pcntvs0600  -406.26    1086.04   329.86  -0.374  0.70859    
# PTSD:ApproxAge    224.69      77.13   362.12   2.913  0.00380 ** 
#
PTSD_IL6  <- lIL6 <- lmer(IL6 ~ PTSD*Pcntvs0 + PTSD*Age_Cat + 
              (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(PTSD_IL6)
# PTSD            -3706.93    1571.39   410.16  -2.359  0.01879 *  
# Pcntvs0200       6469.35     760.20   330.84   8.510 6.14e-16 ***
# Pcntvs0600      13078.15     752.79   323.11  17.373  < 2e-16 ***
# PTSD:Age_Cat2    4248.61    2119.04   364.52   2.005  0.04570 *  
# PTSD:Age_Cat3    7435.05    2280.07   317.98   3.261  0.00123 ** 
# PTSD:Age_Cat4    7862.51    2943.02   305.68   2.672  0.00795 ** 

slopes <- emtrends(PTSD_IL6, ~ Age_Cat, var = "PTSD", cov.red = FALSE)
test(slopes)
#  1            -3958 1450 378  -2.731  0.0066 **
#  2              291 1610 335   0.180  0.8569
#  3             3477 1780 282   1.952  0.0519 *
#  4             3905 2580 290   1.514  0.1312

eff <- ggeffect(PTSD_IL6 , terms = c("PTSD", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL6 ",
       title = "IL6  vs PTSD by Age Category") +
  theme_minimal()
```

#PTSD IL8, visit?
```{r}
#=============================================================================================
IL8 <- lmer(IL8 ~ PTSD*Pcntvs0 + PTSD*ApproxAge + PTSD*Visit_Number + (1|Subject_ID:silanized_LPS:LPS_Batch), data = df2)
summary(IL8) #significant influence of visit #
# PTSD               -300.674    192.842  394.668  -1.559  0.11976    
# Pcntvs0200          301.882     40.241  324.322   7.502 6.09e-13 ***
# Pcntvs0600          593.643     39.851  317.370  14.897  < 2e-16 ***
# ApproxAge             6.305      3.456  137.920   1.824  0.07028 .  
# Visit_Number2        84.080     47.792  409.773   1.759  0.07927 .  
# Visit_Number3        62.071     78.106  424.207   0.795  0.42723    
# PTSD:Pcntvs0200      14.583     57.418  325.471   0.254  0.79967    
# PTSD:Pcntvs0600      54.179     56.989  320.098   0.951  0.34248    
# PTSD:ApproxAge        8.781      4.324  372.395   2.031  0.04296 *  
# PTSD:Visit_Number2 -130.747     66.509  404.076  -1.966  0.05000 .  
# PTSD:Visit_Number3 -355.669    112.388  440.494  -3.165  0.00166 **

slopes <- emtrends(IL8, ~ Visit_Number, var = "PTSD", cov.red = FALSE)
test(slopes)
 # Visit_Number PTSD.trend    SE  df t.ratio p.value
 # 1                 141.0  65.1 378   2.166  0.0309 *
 # 2                  10.2  64.1 376   0.159  0.8736
 # 3                -214.7 110.0 407  -1.952  0.0517 Trend


eff <- ggeffect(IL8 , terms = c("PTSD", "Visit_Number"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL8 ",
       title = "IL8  vs PTSD by Visit") +
  theme_minimal()


```

#PTSD, IL8, Age
```{r}
IL8 <- lmer(IL8 ~ PTSD*Pcntvs0 + PTSD*ApproxAge + 
              (1|Subject_ID/Visit_Number) + (1|LPS_Batch:silanized_LPS), data = df2)
summary(IL8)
# PTSD            -509.651    246.354  158.025  -2.069   0.0402 *  
# Pcntvs0200       295.786     36.405  287.020   8.125 1.34e-14 ***
# Pcntvs0600       580.753     36.405  287.020  15.953  < 2e-16 ***
# ApproxAge          7.318      3.820   67.596   1.916   0.0596 .  
# PTSD:Pcntvs0200    8.174     52.174  293.151   0.157   0.8756    
# PTSD:Pcntvs0600   32.310     52.174  293.151   0.619   0.5362    
# PTSD:ApproxAge    10.979      5.540  146.113   1.982   0.0494 *  

PTSD_IL8 <- lmer(IL8 ~ PTSD*Pcntvs0 + PTSD*Age_Cat + 
              (1|Subject_ID/Visit_Number) + (1|LPS_Batch:silanized_LPS), data = df2)
summary(PTSD_IL8)
# PTSD            -239.415    104.098  132.648  -2.300  0.02302 *  

slopes <- emtrends(PTSD_IL8, ~ Age_Cat, var = "PTSD", cov.red = FALSE)
test(slopes)
 # Age_Cat PTSD.trend  SE    df t.ratio p.value
 # 1           -182.3 106 144.3  -1.726  0.0865
 # 2            -42.8 121 137.5  -0.355  0.7229
 # 3             47.6 123  97.2   0.387  0.6997
 # 4            210.7 186 131.0   1.131  0.2603

eff <- ggeffect(PTSD_IL8 , terms = "PTSD")
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL8 ",
       title = "IL8  vs PTSD") +
  theme_minimal()
```

#PTSD IL10
```{r}

plot(df2$Project, df2$IL10)
#=============================================================================================
IL10 <- lmer(IL10 ~ PTSD*Pcntvs0 + PTSD*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL10)
# #PTSD            -151.318     72.925  317.298  -2.075   0.0388 *  
# Pcntvs0200       113.440     18.126  343.190   6.258 1.16e-09 ***
# Pcntvs0600       166.487     18.007  334.018   9.246  < 2e-16 ***
# ApproxAge          2.989      1.157  129.679   2.582   0.0109 *  
# PTSD:Pcntvs0200    8.992     25.840  345.925   0.348   0.7281    
# PTSD:Pcntvs0600  -16.160     25.715  339.031  -0.628   0.5302    
# PTSD:ApproxAge     3.769      1.620  285.231   2.326   0.0207 *  

PTSD_IL10  <- lmer(IL10  ~ PTSD*Pcntvs0 + PTSD*Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(PTSD_IL10)
#PTSD:Age_Cat4    198.617     60.571 237.503   3.279  0.00120 ** 

eff <- ggeffect(PTSD_IL10 , terms = c("PTSD", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL10 ",
       title = "IL10  vs PTSD by Age Category") +
  theme_minimal()

slopes <- emtrends(PTSD_IL10, ~ Age_Cat, var = "PTSD", cov.red = FALSE)
test(slopes)
 # Age_Cat PTSD.trend   SE  df t.ratio p.value
 # 1            -39.6 30.6 299  -1.293  0.1969
 # 2            -11.6 33.7 298  -0.345  0.7302
 # 3             11.5 36.3 223   0.317  0.7516
 # 4            159.1 52.6 228   3.022  0.0028 **
```


#PTSD TNFalpha
```{r}
#=============================================================================================
TNFalpha <- lmer(TNFalpha ~ PTSD*Pcntvs0 + PTSD*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(TNFalpha) #  ns without age in model
# PTSD            -3449.39    1545.82   386.64  -2.231   0.0262 *  
# Pcntvs0200       3034.53     345.47   331.40   8.784   <2e-16 ***
# Pcntvs0600       5659.97     342.18   323.29  16.541   <2e-16 ***
# ApproxAge          47.10      27.14   134.95   1.735   0.0850 .  
# PTSD:Pcntvs0200   107.62     492.85   332.90   0.218   0.8273    
# PTSD:Pcntvs0600   367.88     489.35   326.74   0.752   0.4527    
# PTSD:ApproxAge     81.77      34.71   358.67   2.356   0.0190 *


PTSD_TNFalpha  <- lmer(TNFalpha  ~ PTSD*Pcntvs0 + PTSD*Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(PTSD_TNFalpha)
# PTSD             -2060.0      705.1   408.2  -2.922 0.003675 ** 
# PTSD:Age_Cat2     3187.8      950.2   361.5   3.355 0.000878 ***
# PTSD:Age_Cat3     3269.6     1021.9   314.0   3.200 0.001517 ** 
# PTSD:Age_Cat4     2810.7     1318.8   301.5   2.131 0.033877 *  

slopes <- emtrends(PTSD_TNFalpha, ~ Age_Cat, var = "PTSD", cov.red = FALSE)
test(slopes)
 # Age_Cat PTSD.trend   SE  df t.ratio p.value
 # 1            -1901  650 376  -2.924  0.0037 **
 # 2             1287  722 334   1.782  0.0757 trend
 # 3             1369  798 280   1.716  0.0873 trend
 # 4              910 1160 287   0.788  0.4316

eff <- ggeffect(PTSD_TNFalpha , terms = c("PTSD", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted TNFalpha ",
       title = "TNFalpha  vs PTSD by Age Category") +
  theme_minimal()

```


#PTSD not significant; IL2, IL4, IL12p70, IL13, IFNgamma
```{r}
#=============================================================================================
IL2 <- lmer(IL2 ~ PTSD*Pcntvs0 +PTSD*ApproxAge + (1|Subject_ID:LPS_Batch:Project), data = df2)
summary(IL2) #trend
#  
#=============================================================================================
IL4 <- lmer(IL4 ~ PTSD*Pcntvs0 +
              (1|Subject_ID/Visit_Number:LPS_Batch:Project:silanized_LPS), 
                 data = df2)
summary(IL4)  
# PTSD             73.8836    32.9938 192.7138   2.239   0.0263 *  
# Pcntvs0200      123.0517    17.1755 286.0126   7.164 6.65e-12 ***
# Pcntvs0600      267.7236    17.1755 286.0126  15.588  < 2e-16 ***
# PTSD:Pcntvs0200   0.4625    24.6073 292.4513   0.019   0.9850    
# PTSD:Pcntvs0600  14.3079    24.6073 292.4513   0.581   0.5614   #Main effect of PTSD; no interaction with age

PTSD_IL4  <- lmer(IL4  ~ PTSD * Pcntvs0 + (1|Subject_ID), data = df2)
eff <- ggeffect(PTSD_IL4 , terms = "PTSD")

eff_df <- as.data.frame(eff)

ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "PTSD",
       y = "Predicted IL4 ",
       title = "IL4  vs PTSD by Age Category") +
  theme_minimal()
#=============================================================================================
IL12p70 <- lmer(IL12p70 ~ PTSD*Pcntvs0 + (1|Subject_ID:Project), data = df2)
summary(IL12p70) # Batch ns 
# 
#=============================================================================================
IL13 <- lmer(IL13 ~ PTSD*Pcntvs0 +  Visit_Number + 
               (1|Subject_ID:LPS_Batch:Project), 
                 data = df2)
summary(IL13) #silanized ns; PTSD ns with or without age; visit # ns
# #=============================================================================================
IFNgamma <- lmer(IFNgamma ~ PTSD*Pcntvs0 + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IFNgamma) #ns
```


#===================================================================================================#
#Negative_Affect NS IL1beta, IL2, IL4, IL8, IL10, IL12p70, TNFalpha, IFNgamma
```{r}
IL1beta <- lmer(IL1beta ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge + 
                  (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL1beta) #ns with or without age
#=============================================================================================
IL2 <- lmer(IL2 ~ Negative_Affect*Pcntvs0 + 
              (1|Subject_ID:LPS_Batch:Project), data = df2)
summary(IL2) # ns with or without age
#=============================================================================================
# ns with or without age
#=============================================================================================
IL8 <- lmer(IL8 ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge + Visit_Number +
              (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL8)

IL8 <- lmer(IL8 ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge + 
              (1|Subject_ID/Visit_Number) + (1|LPS_Batch:silanized_LPS), data = df2)
summary(IL8) #ns
#=============================================================================================
Negative_Affect_IL10  <- lmer(IL10  ~ Negative_Affect * Pcntvs0 + Negative_Affect * Age_Cat + (1|Subject_ID), data = df2)
summary(Negative_Affect_IL10)
#=============================================================================================

IL12p70 <- lmer(IL12p70 ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge + (1|Subject_ID:LPS_Batch:Project), data = df2)
summary(IL12p70) #ns with or wihtout age
#=============================================================================================
TNFalpha <- lmer(TNFalpha ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge + 
                   (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(TNFalpha) #  ns with or without age
#=============================================================================================
IFNgamma <- lmer(IFNgamma ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge +
                   (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IFNgamma) #ns with or without age
# 
```

#Neg Affect IL6, Dose, Age
```{r}
#=============================================================================================
IL6 <- lmer(IL6 ~ Negative_Affect*Pcntvs0 + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL6)  
#Negative_Affect:Pcntvs0600  -1590.6      952.9   313.3  -1.669   0.0961 . 

Negative_Affect_IL6 <- lmer(IL6 ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge +
              (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(Negative_Affect_IL6)
# Negative_Affect            -7493.25    3142.99   234.22  -2.384 0.017918 *  
# Pcntvs0200                  6476.78     761.04   332.93   8.510    6e-16 ***
# Pcntvs0600                 13096.77     754.70   325.62  17.354  < 2e-16 ***
# ApproxAge                    -46.20      57.98   129.44  -0.797 0.427038    
# Negative_Affect:Pcntvs0200  -676.15     959.00   320.50  -0.705 0.481285    
# Negative_Affect:Pcntvs0600 -1625.33     951.40   313.48  -1.708 0.088561 .  
# Negative_Affect:ApproxAge    155.55      66.83   226.36   2.328 0.020812 *


Negative_Affect_IL6 <- lmer(IL6 ~ Negative_Affect*Pcntvs0 + Negative_Affect*Age_Cat +
              (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(Negative_Affect_IL6)
# Negative_Affect            -3143.62    1528.63   242.94  -2.056   0.0408 *  
# Pcntvs0200                  6477.59     760.81   330.86   8.514 5.97e-16 ***
# Pcntvs0600                 13098.54     754.58   323.78  17.359  < 2e-16 ***
# Age_Cat2                     -68.72    1753.05   244.58  -0.039   0.9688    
# Age_Cat3                     423.39    1989.31   175.40   0.213   0.8317    
# Age_Cat4                   -2770.86    2068.58   136.95  -1.340   0.1826    
# Negative_Affect:Pcntvs0200  -676.47     958.69   318.44  -0.706   0.4809    
# Negative_Affect:Pcntvs0600 -1634.01     951.16   311.40  -1.718   0.0868 .  
# Negative_Affect:Age_Cat2    1750.34    2412.33   246.77   0.726   0.4688    
# Negative_Affect:Age_Cat3    5278.72    2276.96   268.60   2.318   0.0212 *  
# Negative_Affect:Age_Cat4    3716.51    2522.23   181.35   1.474   0.1423   

slopes <- emtrends(Negative_Affect_IL6, ~ Age_Cat, var = "Negative_Affect", cov.red = FALSE)
test(slopes)
 # Age_Cat Negative_Affect.trend   SE  df t.ratio p.value
 # 1                       -3914 1440 202  -2.718  0.0071 **
 # 2                       -2163 1960 280  -1.106  0.2698
 # 3                        1365 1780 331   0.767  0.4434
 # 4                        -197 2080 181  -0.095  0.9246

eff <- ggeffect(Negative_Affect_IL6 , terms = c("Negative_Affect", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Negative_Affect",
       y = "Predicted IL6 ",
       title = "IL6  vs Negative_Affect by Age Category") +
  theme_minimal()

```


#neg affect IL13, Age
```{r}
#=============================================================================================
Negative_Affect_IL13 <- lmer(IL13 ~ Negative_Affect*Pcntvs0 + Negative_Affect*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(Negative_Affect_IL13)
# Negative_Affect             76.5540    35.4260 248.3223   2.161   0.0317 *  
# Pcntvs0200                  32.8017     8.2946 332.8371   3.955 9.37e-05 ***
# Pcntvs0600                  76.5956     8.2211 325.9417   9.317  < 2e-16 ***
# ApproxAge                    1.2974     0.6627 133.1082   1.958   0.0524 .  
# Negative_Affect:Pcntvs0200  -3.5160    10.4425 321.3103  -0.337   0.7366    
# Negative_Affect:Pcntvs0600  -6.3040    10.3543 314.6435  -0.609   0.5431    
# Negative_Affect:ApproxAge   -1.5865     0.7537 241.7593  -2.105   0.0363 * 

Negative_Affect_IL13 <- lmer(IL13 ~ Negative_Affect*Pcntvs0 + Negative_Affect*Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(Negative_Affect_IL13)
# Negative_Affect              25.361     17.285 252.340   1.467   0.1436    
# Pcntvs0200                   32.839      8.279 329.544   3.966 8.96e-05 ***
# Pcntvs0600                   76.804      8.206 322.953   9.359  < 2e-16 ***
# Age_Cat2                     18.155     19.813 259.197   0.916   0.3604    
# Age_Cat3                     -1.849     22.688 181.952  -0.081   0.9352    
# Age_Cat4                     54.947     23.754 140.954   2.313   0.0222 *  


slopes <- emtrends(Negative_Affect_IL13, ~ Age_Cat, var = "Negative_Affect", cov.red = FALSE)
test(slopes)
 # Age_Cat Negative_Affect.trend   SE  df t.ratio p.value
 # 1                       22.08 16.4 213   1.349  0.1788
 # 2                       19.82 22.0 294   0.899  0.3693
 # 3                       -8.72 19.9 352  -0.438  0.6620
 # 4                      -20.72 23.7 190  -0.873  0.3840

eff <- ggeffect(Negative_Affect_IL13 , terms = c("Negative_Affect", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Negative_Affect",
       y = "Predicted IL13 ",
       title = "IL13  vs Negative_Affect by Age Category") +
  theme_minimal()
```
#=
#===================================================================================================#
#===================================================================================================#
#INSOMNIA IL1beta
```{r}
#=============================================================================================
IL1beta <- lmer(IL1beta ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL1beta) 
# Insomnia            -1471.988    696.298   236.396  -2.114  0.03556 *  
# Pcntvs0200           1015.692    147.078   324.153   6.906 2.64e-11 ***
# Pcntvs0600           1702.411    145.802   315.862  11.676  < 2e-16 ***
# ApproxAge               4.419     11.377   123.312   0.388  0.69840    
# Insomnia:Pcntvs0200    23.148    200.250   330.583   0.116  0.90804    
# Insomnia:Pcntvs0600  -112.257    198.827   323.536  -0.565  0.57274    
# Insomnia:ApproxAge     32.486     15.239   243.949   2.132  0.03402 *


IL1beta <- lmer(IL1beta ~ Insomnia*Pcntvs0 + Insomnia*Age_Cat + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL1beta) 
# Insomnia             -433.49     292.18  280.53  -1.484    0.139    
# Insomnia:Age_Cat4    1269.41     518.19  246.67   2.450    0.015 *  

slopes <- emtrends(IL1beta, ~ Age_Cat, var = "Insomnia", cov.red = FALSE)
test(slopes)
 # Age_Cat Insomnia.trend  SE  df t.ratio p.value
 # 1                 -464 270 239  -1.717  0.0873
 # 2                 -109 336 320  -0.326  0.7449
 # 3                  143 326 389   0.439  0.6609
 # 4                  805 445 274   1.810  0.0715


eff <- ggeffect(IL1beta, terms = c("Insomnia", "Age_Cat"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Insomnia",
       y = "Predicted IL1beta",
       title = "IL1beta vs Insomnia by Age Category") +
  theme_minimal()
```

#Insomnia NS IL2, IL4, IL6, IL10, IL13, TNFalpha, IFNgamma
```{r}
#=============================================================================================
IL2 <- lmer(IL2 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch), data = df2)
summary(IL2) #
#=============================================================================================
IL4 <- lmer(IL4 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL4) # 
#=============================================================================================
IL6 <- lmer(IL6 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL6)
#=============================================================================================
IL10 <- lmer(IL10 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL10)
#=============================================================================================
IL13 <- lmer(IL13 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge +  (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL13)
#=============================================================================================
TNFalpha <- lmer(TNFalpha ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(TNFalpha) #  
#=============================================================================================
IFNgamma <- lmer(IFNgamma ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IFNgamma)
```

#Insomnia
```{r}
#=============================================================================================
IL8 <- lmer(IL8 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + Insomnia*Visit_Number + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL8)
# # Insomnia            -385.246    203.565  267.974  -1.892  0.05950 .  
# Pcntvs0200           298.988     40.521  328.086   7.379 1.32e-12 ***
# Pcntvs0600           585.179     40.155  321.300  14.573  < 2e-16 ***
# ApproxAge              5.443      3.412  135.762   1.595  0.11293    
# Visit_Number2         91.157     46.891  402.384   1.944  0.05259 .  
# Visit_Number3        189.174     61.968  425.401   3.053  0.00241 ** 
# Insomnia:Pcntvs0200  -10.286     55.211  333.066  -0.186  0.85232    
# Insomnia:Pcntvs0600  -13.150     54.772  326.873  -0.240  0.81041    
# Insomnia:ApproxAge     7.955      4.454  277.995   1.786  0.07519 .   

IL8 <- lmer(IL8 ~ Insomnia*Pcntvs0 + Insomnia*ApproxAge + (1|Subject_ID/Visit_Number) + (1|LPS_Batch:silanized_LPS), data = df2)
summary(IL8)
# Insomnia            -268.255    232.461  103.518  -1.154   0.2512    
# Pcntvs0200           311.995     36.384  300.987   8.575  5.3e-16 ***
# Pcntvs0600           589.782     35.979  310.635  16.393  < 2e-16 ***
# ApproxAge              5.223      3.410   62.592   1.532   0.1306    
# Insomnia:Pcntvs0200    5.491     44.739  296.283   0.123   0.9024    
# Insomnia:Pcntvs0600  -13.540     44.732  296.420  -0.303   0.7623    
# Insomnia:ApproxAge     4.483      5.142  101.944   0.872   0.3853  

```

#Insomnia, IL12p70
```{r}
#=============================================================================================
Insomnia_IL12p70 <- lmer(IL12p70 ~ Insomnia*Pcntvs0 + (1|Subject_ID:LPS_Batch), data = df2)
summary(Insomnia_IL12p70)
# Insomnia               20.35      25.51 345.14   0.798   0.4256    
# Pcntvs0200            113.57      15.63 345.39   7.265 2.50e-12 ***
# Pcntvs0600            175.84      15.63 345.39  11.249  < 2e-16 ***
# Insomnia:Pcntvs0200    33.56      20.91 345.39   1.605   0.1094    
# Insomnia:Pcntvs0600    42.66      20.91 345.39   2.040   0.0421 *  

slopes <- emtrends(Insomnia_IL12p70, ~ Pcntvs0, var = "Insomnia", cov.red = FALSE)
test(slopes)
 # Pcntvs0 Insomnia.trend   SE  df t.ratio p.value
 # 70                20.3 25.6 346   0.794  0.4279
 # 200               53.9 25.6 346   2.103  0.0362 *
 # 600               63.0 25.6 346   2.458  0.0145 *

eff <- ggeffect(Insomnia_IL12p70 , terms = c("Insomnia", "Pcntvs0"))
eff_df <- as.data.frame(eff)
ggplot(eff_df, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  facet_wrap(~ group, nrow = 1) +
  labs(x = "Insomnia",
       y = "Predicted IL12p70 ",
       title = "IL12p70  vs Insomnia by Pcntvs0") +
  theme_minimal()
```

#===================================================================================================#
#Anxiety #Not used in poster
```{r}
#=============================================================================================
IL1beta <- lmer(IL1beta ~ Anxiety*Pcntvs0 +Anxiety*ApproxAge + 
                   (1|Subject_ID:LPS_Batch:silanized_LPS), 
                 data = df2)
summary(IL1beta) #Trends for anxieyt and Anxiety*ApproxAge
#======================================================================
IL2 <- lmer(IL2 ~ Anxiety*Pcntvs0 + Anxiety*ApproxAge + (1|Subject_ID:LPS_Batch:Project), data = df2)
summary(IL2) #ns
#  
#=============================================================================================
IL4 <- lmer(IL4 ~ Anxiety*Pcntvs0 + Anxiety*ApproxAge + (1|Subject_ID:LPS_Batch:Project:silanized_LPS), 
                 data = df2)
summary(IL4) # Anxiety:Pcntvs0600:Gender2   148.80      68.32 333.44   2.178 0.030103 *  no interactiosn between anxiety and visit
#
IL4 <- lmer(IL4 ~ Anxiety*Pcntvs0 + Anxiety*ApproxAge + (1|Subject_ID:LPS_Batch:Project:silanized_LPS), 
                 data = df2)
summary(IL4) #ns
#
#=============================================================================================
IL6 <- lmer(IL6 ~ Anxiety*Pcntvs0 + (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(IL6) #Anxiety:Pcntvs0600 -1739.37     979.13   321.04  -1.776   0.0766 . 
#
#=============================================================================================
IL8 <- lmer(IL8 ~ Anxiety*Pcntvs0 + Anxiety*Visit_Number +(1|Subject_ID:LPS_Batch:silanized_LPS), 
                 data = df2)
summary(IL8)
# Anxiety:Visit_Number3 -347.505     88.489  438.117  -3.927 9.98e-05 ***
IL8 <- lmer(IL8 ~ Anxiety*Pcntvs0 + (1|Subject_ID/Visit_Number) + (1|LPS_Batch:silanized_LPS), 
                 data = df2)
summary(IL8) #ns
#
#=============================================================================================
IL10 <- lmer(IL10 ~ Anxiety*Pcntvs0 + (1|Subject_ID:LPS_Batch:Project:silanized_LPS), data = df2)
summary(IL10)
#
#=============================================================================================
IL12p70 <- lmer(IL12p70 ~ Anxiety*Pcntvs0 + (1|Subject_ID:LPS_Batch:Project), 
                 data = df2)
summary(IL12p70)
# 
#=============================================================================================
IL13 <- lmer(IL13 ~ Anxiety*Pcntvs0 + Anxiety*ApproxAge + (1|Subject_ID:LPS_Batch:Project:silanized_LPS), 
                 data = df2)
summary(IL13)
# 
#=============================================================================================
TNFalpha <- lmer(TNFalpha ~ Anxiety*Pcntvs0 + Anxiety*ApproxAge +  (1|Subject_ID:LPS_Batch:silanized_LPS), data = df2)
summary(TNFalpha) #  

#=============================================================================================
IFNgamma <- lmer(IFNgamma ~ Anxiety*Pcntvs0+ Anxiety*ApproxAge +  (1|Subject_ID:LPS_Batch:silanized_LPS), 
                 data = df2)
summary(IFNgamma)
# Anxiety            -53.4159    27.4331 308.5337  -1.947  0.05243 .  
# Pcntvs0200          25.8683     6.7412 322.5601   3.837  0.00015 ***
# Pcntvs0600          33.2488     6.6829 313.9634   4.975 1.08e-06 ***
# ApproxAge            1.4850     0.5154 125.8091   2.881  0.00466 ** 
# Anxiety:Pcntvs0200  -2.9521     8.5837 314.9722  -0.344  0.73114    
# Anxiety:Pcntvs0600   4.0714     8.5283 308.7962   0.477  0.63342    
# Anxiety:ApproxAge    1.3436     0.6114 306.2894   2.197  0.02874 *  
```
#===================================================================================================#
